Best Practices for Single Alchemical Free Energy Calculations [Article v\versionnumber]

### 2025-05-23 paper/manuscript.tex
Clarify meaning of co-alchemical transformation for ions

Alchemical transformations that involve net charge changes can provide difficulties for membrane systems; phospholipids carry functional groups with nonzero formal charge and cannot be treated as a solvent with a uniform dielectric in the same way as water. Several approaches are reviewed in \cite{wu2022correction-51c} and the recommended method is to use a co-alchemical ion to maintain system neutrality.

>>>>

Alchemical transformations that involve net charge changes can provide difficulties for membrane systems; phospholipids carry functional groups with nonzero formal charge and cannot be treated as a solvent with a uniform dielectric in the same way as water. Several approaches are reviewed in \cite{wu2022correction-51c}. The authors recommend the use of charge transfer by making an ion of equivalent charge appear alongside the disappearing charged molecule to maintain system neutrality.
